---
title: "Bad Plot"
author: "Brandon"
date: "3/11/2022"
output: 
  html_document:
    TOC: TRUE
    TOC_FLOAT: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "../Output/")
```

## Intro

Features: 

** This is a plot showing the location of CNG fuels in California using a map plot. 
** Filter and select were used to extract the specific data I wanted.
** Geom polygon to add the map plot, colors made to fit the dog theme 
** Geom point to add the points
** Geom dog to add the dogs, size was made to be larger to cover points 
** Coord fixed to fix the coordinates 
** Titles purposely made terrible 
** Themes purposely made terrible, panel color white


```{r}
library(tidyverse)
library(here)
library(mapproj)
library(maps)
library(mapdata)
library(ggdogs)
```

## Dataset

```{r, echo=FALSE}
stations <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-03-01/stations.csv')
View(stations)
```
## Data Analysis
```{r}
California<-map_data("state", region = "california") #Map of California

Fuel<-stations%>% #Naming data and filtering for specifically CA and CNG fuel
  filter(STATE == "CA",
         FUEL_TYPE_CODE == "CNG")%>% 
  select(LONGITUDE, # Selecting columns
         LATITUDE,
         FUEL_TYPE_CODE)
View(Fuel)
```
## Mapping
```{r BAD1}
ggplot()+
  geom_polygon(data = California, #making polygon plot
               aes(x = long,
                   y = lat),
               fill = "white",
               color = "black")+ # Dog friendly colors
  geom_point(data = Fuel,
             aes(x = LONGITUDE,
                 y = LATITUDE,
                 color = FUEL_TYPE_CODE))+
  geom_dog(data = Fuel, # Adding the Pugs
           aes(x = LONGITUDE,
               y = LATITUDE,
               color = FUEL_TYPE_CODE,
               dog = "pug", size = 1000))+
  coord_fixed()+ # fixing coordinates
  labs(title = "Pug Friendly Fuel Stations in California",
       x = "X-Axis", #appropriate labeling
       y = "Y-Axis",
       color = "Legend",
       caption = "Caption")+
  theme(plot.title = element_text(hjust = 3.0), # proper themes to easily see the plot
        panel.border = element_rect(fill = NA,
                                    color = "white"))+
  theme_void()+
  theme_dark()+
  theme_minimal()+
  scale_color_manual(values = "black") 
```







